Robotic models of learning and development \\of speech and tool use.

### 2015-10-07 roadmap/doc.tex
module choices

	\subsection{SAGG-RIAC}

		Here I want to study the important parameters of the SAGG-RIAC implementation 
		(from Explauto, with my implementation of RIAC in explauto.interest\_model.tree) and test them first on very simple environments.
		The goal is to get a sound progress output, that could be compared with other models' progresses.

@@

>>>>

	\subsection{SAGG-RIAC}
	\label{sec:saggriac}
		Here I want to study the important parameters of the SAGG-RIAC implementation 
		(from Explauto, with my implementation of RIAC in explauto.interest\_model.tree) and test them first on very simple environments.
		The goal is to get a sound progress output, that could be compared with other models' progresses.

@@

	\subsection{Implementation of multiple options to explore a given sensori space}
	\label{choices}

		\paragraph{}
		I have implemented the possibility to have different modules that learn a mapping towards the same sensori space.
		A higher module that uses that space as a motor space will choose which lower module to use to explore a point in that space with the goal to maximize the competence around that point.
		I have tested that idea using SAGG-Random modules instead of SAGG-RIAC ones.
		I compute the progresses (to choose the module that will babble) as the derivative of the competence of last goal babbled points.
		The competence around a point (to choose the module that will reach the goal with the maximum precision) is computed as the mean of the competences of the $k=20$ nearest neighbors.

		\paragraph{}
		The hierarchy used is the following: mod1 learns from $m1$ to $s1$, mod2 learns from $m2$ to $s1$, and mod3 learns from $s1$ to $s2$.
		Mod3 can thus reuse either mod1 or mod2. All spaces are 1-dimensional with range $[0-1]$. Here are the forward models:

		$$s1 = \frac{2*m1 + m2}{3}$$
		$$s2 = s1^2$$

		Thus, if mod3 reuses mod1, it will reach a wider range of outputs than with mod2. Fig. \ref{fchoices} shows the results of 2000 iterations with this setup.
		Mod3 quickly (100 iterations) gets to use mod1 (around 90\% of babbling iterations) instead of mod2.
		In the computation of competences, I also cut the competences to a minimal competence value (or maximal error distance of $0.1$) in order to avoid big random fluctuations of interest (absolute value of progress) 
		when a module wants to explore a far unreachable point, which entails a very high interest (see Sec. \ref{sec:saggriac}).

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/choice_test_choices.png}
			\includegraphics[width=8cm]{./include/choice_test_competences.png}
			%\includegraphics[width=8cm]{./include/choice_test_progresses.png}
			\caption{Progress on the 3 modules of a hierarchy with 2 choices of sub-modules for module 3. Left: Proportion of choices of module 3 (with a sliding window). Right: Competences (with a sliding window) babbled points of each modules.}
			\label{fchoices}
		\end{figure}
